A multi-scale story of the diffusion of a new technology: the web

### 2025-01-21 paper/submission2/response.qmd

"shied away" has been replaced in the opening paragraph.

\color{teal}
\noindent 2. Introduction\
\noindent 2. General Diffusion Studies: The statement that there are few contemporary general diffusion studies in Economic Geography is not accurate, although it may apply specifically to digital technologies. Consider the following recent examples:
o Peris, A., Meijers, E., & van Ham, M. (2021). Information diffusion between Dutch cities: Revisiting Zipf and Pred using a computational social science approach. Computers, Environment and Urban Systems, 85(November), 101565. https://doi.org/10.1016/j.compenvurbsys.2020.101565
o Bednarz, M., & Broekel, T. (2020). Pulled or pushed? The spatial diffusion of wind energy between local demand and supply. Industrial and Corporate Change, 29(4), 893–916. https://doi.org/10.1093/icc/dtaa012
o Feldman, M. P., Kogler, D. F., & Rigby, D. L. (2015). rKnowledge: The Spatial Diffusion and Adoption of rDNA Methods. Regional Studies, 49(5), 798–817. https://doi.org/10.1080/00343404.2014.980799
\color{black}

@PERIS2021101565 is indeed an interesting paper, but it is not directly relevant 
as it focuses on information diffusion rather than diffusion of new 
technologies. Information diffuses through social and, consequently, urban 
networks, but it is not adopted like new technologies. @bednarz2020pulled was 
already cited and @feldman2015rknowledge has now been added. These references 
are included in the second section.

Regarding the statement about economic geography studies on diffusion of 
new technologies and innovation, respectfully, I do believe that this is a fair
statement. The references listed below are the ones reviewed in the second 
section and none of them are published in one of the flagship economic geography
journals (*Journal of Economic Geography* and *Economic Geography*). There are 
two papers published in *The Professional Geographer*, which is a broad-scope
geography journal and then only one paper in *Regional Studies*, which is the 
closest to economic geography. Importantly though, the *Regional Studies* paper 
[@feldman2015rknowledge] paper is focused on inventions as observed by patent 
data contrary to the broader 'adoption of a new technology' approach of this 
paper. All other papers listed below are published in business and economics 
journals.

1. @beardsell1999spatial: *European Economic Review*
2. @bednarz2020pulled: *Industrial and Corporate Change*
3. @haller2011determinants: *Applied Economics*
4. @perkins2011internet: *The Professional Geographer*
5. @feldman2015rknowledge: *Regional Studies*
6. @ding2010modeling: *The Professional Geographer*
7. @bakher2013diffusion: *Journal of Marketing Analytics*
8. @PAPAGIANNIDIS2015308: *Technological Forecasting and Social Change*
9. @lengyel2020role: *Scientific reports*

@@

**HAVE A THINK, intro has been restructured**

\color{teal}
\noindent 5. Structure and Focus: The discussion on motivations should be streamlined and clarified. For example, after specifying that the study focuses on commercial websites rather than the web, subsequent references revert to the general term “web.” Additionally, the discussion confuses diffusion patterns, firm perspectives, and early adopter advantages. Consider restructuring this section to clearly differentiate between literature gaps (motivations) and expected outcomes (mechanisms).
\color{black}

The revised paper consistently illustrates that the focus is on commercial 
websites.

In the relevant paragraph in the Data and Methods section, the following line
has been added: "Henceforward any reference to websites will refer to commercial 
-- .co.uk -- websites".

@@

\color{teal}
\noindent 3. Lack of Hypotheses: To clarify what the paper delivers and what knowledge gaps it fills, I strongly recommend developing a number of hypotheses that will be tested.
\color{black}

Added.

\color{teal}
\noindent 4. Fit to title: The term “multi-scalar” appears in the title but is never really discussed in the paper.
\color{black}

This was discussed from the data section onwards, but indeed not before that. 
Section 2 includes a new paragraph describing the second hypothesis (H~2~), 
which explicitly discusses the value of the multiscale approach: 
"Understanding the diffusion of a new technology in multiple, detailed spatial
scales is of interest to economic geography as ..."

@@

**growth as an appendix, spatial dependencies have been included**

\color{teal}
\noindent 5. Results\
\noindent 1. Diffusion Speed: The decision to binarize diffusion speed is questionable. Continuous measures, such as growth rates or the time required to reach 50% saturation, would provide more informative insights.
\color{black}

**This is only for the map, this is a critical point in diffusion studies**

H1: first descriptives, then modelling
- S curves
Figure 1: UK curve, Figure 2: some LAD curves. link to a gif. 
keep fast slow map, briefly touch upon and say it will be further discussed below
- neighbourhood
- hierarchy
- modelling

H2: link map with ranks. Explore OA stability within LADs

@@

\color{teal}
\noindent 2. Geographical Scale: While the effort to model diffusion curves at a fine geographical scale is commendable, the paper does not sufficiently explain the benefits or additional knowledge gained from this approach.
\color{black}

**reveal that theories are valid for local scales and inform local tech policies**

### 2025-01-21 paper/submission2/tranos2025.qmd
paper

> H~2~: The diffusion of the commecrial Web is shaped by both early adoption 
and late comer effects.

@@

<!-- rankings -->
The next step assesses the stability and volatility of the LAD in terms
of their adoption of web technologies. As highlighted in the literature
[@risk_perceptions], different agents have different perceptions about
and levels of acceptance of the risks and the potential economic returns
associated with the adoption of new technologies -- see for instance the
seminal work of @venkatesh2000theoretical. To reveal such aggregated
patterns, Figure \ref{rank} plots the ranking of UK LAD based on website
density. To decrease noise, the average ranking of 1996-1998 and
2010-2012 is plotted instead of the individual years. The colours depict
the 5th and 95th percentile of the absolute difference of the LAD
ranking between 1996-1998 and 2010-2012. While there are quite a few
obvious cases of LAD that maintained their position between the
beginning and the end of the study period both at the top or at the
bottom of the hierarchy, there are also quite a few LAD that changed
drastically their position. Some of these LAD enjoyed a process that at
the first instance looks like *leapfrogging* since they managed to jump
at the top of the hierarchy despite their slow start. There is extensive
literature regarding the potential benefits of technological
leapfrogging. The underpinning argument is that latecomers can adopt and
benefit from new technologies that have been developed elsewhere without
incurring the hefty initial R&D costs [@teece2008firm]. Although the
leapfrogging literature does not pay much attention to cities and
regions [@yu2018sustainability], previous research highlighted the long
term and sustained productivity benefit of the early adopters of web
technologies in the UK [@tranosuk]. So, although the LAD system is
volatile, it is not clear whether the LAD with high concentration of
late adopters will gain any latecomer-related benefits in a way similar
to countries experiencing technological leapfrogging. Still, the
opportunity to catch up that @perkins2005international illustrated at
the country level, is also visible at the much more detailed LAD scale.
As previously, this is consistent with including websites with up to 10
postcodes (see Figure \ref{rank10}).

@@

>>>>

> H~2~: The diffusion of the commercial Web is shaped by both early adoption 
and late comer effects.

@@

@@

## H2

<!-- H~2~: The diffusion of the commercial Web is shaped by both early adoption  -->
<!-- and late comer effects. -->

To test the second hypothesis (H~2~) the stability and volatility of the LAD 
in terms of their adoption of the Web is assessed. As highlighted in 
the literature [@risk_perceptions], different agents have different perceptions 
about and levels of acceptance of the risks and the potential economic returns
associated with the adoption of new technologies -- see for instance the
seminal work of @venkatesh2000theoretical. To reveal such aggregated
patterns, Figure \ref{rank} plots the ranking of UK LAD based on website
density. To decrease noise, the average ranking of 1996-1998 and
2010-2012 is plotted instead of the individual years. The colours depict
the 5th and 95th percentile of the absolute difference of the LAD
ranking between 1996-1998 and 2010-2012. While there are quite a few
obvious cases of LAD that maintained their position between the
beginning and the end of the study period both at the top or at the
bottom of the hierarchy, there are also quite a few LAD that changed
drastically their position. Some of these LAD enjoyed a process that at
the first instance looks like *leapfrogging* since they managed to jump
at the top of the hierarchy despite their slow start.

There is extensive
literature regarding the potential benefits of technological
leapfrogging. The underpinning argument is that latecomers can adopt and
benefit from new technologies that have been developed elsewhere without
incurring the hefty initial R&D costs [@teece2008firm]. Although the
leapfrogging literature does not pay much attention to cities and
regions [@yu2018sustainability], previous research highlighted the long
term and sustained productivity benefit of the early adopters of web
technologies in the UK [@tranosuk]. So, although the LAD system is
volatile, it is not clear whether the LAD with high concentration of
late adopters will gain any latecomer-related benefits in a way similar
to countries experiencing technological leapfrogging. Still, the
opportunity to catch up that @perkins2005international illustrated at
the country level, is also visible at the much more detailed LAD scale.
As previously, this is consistent with including websites with up to 10
postcodes (see Figure \ref{rank10}).
